Paper Report

### 2017-11-16 Paper_report.tex
save

\begin{equation}
p(f_1^J|e_1^I) = \sum_{a_1^J} p(f_1^J, a_1^J|e_1^I)
\end{equation}

@@

@@

\section{Word alignment model in Neural Network}
We start from this formula \eqref{Och2003Systematic Alignment Model Equation}:

\begin{equation}
p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
\label{Word Alignment Model Neural Network HMM Equation}
\end{equation}

In general, we try to calculate these probability by using two different neural networks.
The significant point of NN is embedding context.

\subsection{Probability approach}
Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM. \eqref{Word Alignment Model Neural Network HMM Equation} becomes:
\begin{equation}
p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
\end{equation}

>>>>

\begin{equation}
\end{equation}

@@

\begin{equation}
p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)
\label{Overview about Statistical Alignment p(f,e)}
\end{equation}

@@

\section{Word alignment model in Neural Network}
We start from this formula \eqref{Overview about Statistical Alignment p(f,e)}:

\begin{equation}
p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)
\label{Word Alignment Model Neural Network p(f,e)}
\end{equation}

\subsection{Probability approach}
Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM. In general, we try to calculate the probability by using two different neural networks.The significant point of NN is embedding context.

They use Generalized EM to estimate $\theta$, \eqref{Word Alignment Model Neural Network p(f,e)} becomes:

$p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)$ \\

$ = E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ] + H[q(a_1^J)] + KL(q(a_1^J) \| p_{\theta}(a_1^J|f_1^J,e_1^I) ) $ \\

Updating $\theta$ requires only maximizing $E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ]$. The gradient is: \\
\marginpar{Why?: See \citep{Tran16unsupervised}}

$ J(\theta) = \sum_{a_1^J} \quad q(a_1^J)\quad ln \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $
